A highly-available move operation for replicated trees

### 2019-11-03 paper/move-op.tex
paper: final fiddling
More rewording of closing paragraph.

As mentioned in the introduction, the work presented in this paper is especially interesting due to the ubiquity of the tree-structured data model across a range of different computing systems.
In future work we hope to build novel peer-to-peer distributed systems, such as a distributed file-system, that make use of our algorithm.

>>>>

As mentioned in the introduction, our work is especially interesting due to the ubiquity of the tree-structured data model across a range of different computing systems.
In future work we hope to build novel peer-to-peer distributed systems, such as a distributed file-system, that make use of our algorithm.
